ERNIE: Supporting Collaboration Studies in Multiple Domains

### 2017-12-05 LaTeX/Paper2/paper2.tex

\title{XX}
%\tnotetext[mytitlenote]{This document is a collaborative effort}

%% Group authors per affiliation:
%% or include affiliations in footnotes:
\author[nl]{Samet Keserci}

\author[nl]{Avon Davey}

\author[ca]{Di Cross}

\author[gi]{Alexander R. Pico}

\author[nl]{George Chacko \corref{cor1}}
\ead{netelabs@nete.com}

@@

\address[nl]{NETE Labs, NET ESolutions Corporation, McLean, VA, USA}
\address[cal]{XX, USA}
\address[gi]{Gladstone Institutes, San Francisco, CA, USA}

\raggedright
\begin{abstract}
\end{abstract}

@@

\section*{Results and Discussion} 
\section*{Acknowledgments} This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow from the University of Illinois Urbana-Champaign for critical comments and advice on formalizing definitions. We also thank Sandeep Somaiya and Syd Gomes from NETE as well as Holly J. Falk-Krzesinski, Daniel Calto, M'hamed Aisati, and Sherif El Shamy from Elsevier for their support of this collaboration.

>>>>

\title{ERNIE: Supporting Collaboration Studies in Multiple Domains} 
%\tnotetext[mytitlenote]{This document is a collaborative effort}

%% Group authors per affiliation:
%% or include affiliations in footnotes:
\author[nl]{Samet Keserci}
\author[nl]{Avon Davey}
\author[ca]{Di Cross}
\author[gi]{Alexander R. Pico}
\author[nl]{Dmitriy Korobskiy}
\author[nl]{George Chacko \corref{cor1}}
\ead{netelabs@nete.com}

@@

\address[nl]{NETE Labs, NET ESolutions Corporation, McLean, VA, USA}
\address[ca]{XX, USA}
\address[gi]{Gladstone Institutes, San Francisco, CA, USA}

\raggedright

\begin{abstract}

Data mining of public and commercially available data sources coupled with network analysis has been used as a digital methodology to document and analyze collaboration and knowledge flow in the development of a drug. This approach is extensible to research evaluation problems in any scientific area that can be defined by a nucleus of publications with accessible citation records. However, a tradeoff exists between exhaustive manual curation by experts and automated `big-data' methods. The former is less scalable, the latter can be less accurate. We have developed Enhanced Research Network Information Environment (ERNIE), a cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones. ERNIE is built using Open Source tools, is easily replicated and modified, and its modular design enables the facile addition of new data sources and deletion or substitution of existing ones. Data in ERNIE can be accessed using search technologies or Structured Query Language (SQL). To demonstrate the capabilities of ERNIE we present the results of seven case studies that span drug development, pharmacogenomics, behavioral interventions, and opioid addiction. In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases as well as  clinical trials to document collaborations and identify influential research accomplishments.

\end{abstract}

@@

\section*{Results and Discussion} 
\section*{Acknowledgments} XX
